---
title: "Fastqc Report"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
toc_depth: 4
number_sections: true
theme: lumen
params:
  read1_before_dir: ""
  read1_after_dir: ""
  read2_before_dir: ""
  read2_after_dir: ""
  cutadapt_cmd: ""
---

```{r include=FALSE}
library(tidyverse)
library(scales)
library(plotly)

plot_quality <- function(d){
    d %>% plot_ly(type="box", 
                  q1=~`Lower Quartile`, 
                  median=~Median,
                  q3=~`Upper Quartile`, 
                  lowerfence=~`10th Percentile`, 
                  upperfence=~`90th Percentile`, 
                  line = list(color="#6060B0"), name="") %>% 
        add_lines(x=~Base, y=~Mean, line=list(color="#6E6E3C"), name="") %>% 
        layout(yaxis = list(range = c(0, 40), title="Quality"), showlegend = FALSE)
}

plot_nt_distribution <- function(d){
    d <- d %>% pivot_longer(-Base, names_to = "nt", values_to = "percent")
    p <- ggplot(d, aes(Base, percent, color=nt))+
        geom_line(alpha=0.8) + ylim(0,100) + theme_bw()+ 
        theme(
            axis.text.x = element_text(face = "bold", color = "black"), 
            panel.grid = element_blank(),
            legend.title = element_blank(),
            legend.position = "top"
        ) + scale_color_brewer(palette = "Set1")
    ggplotly(p) %>% layout(legend = list(x=0.9, y=0.95, title = ""))
}

plot_length <- function(d){
    p <- ggplot(d, aes(Length, Count))+
        geom_line(alpha=0.8) + theme_bw()+
        theme(
            axis.text.x = element_text(face = "bold", color = "black"),
            panel.grid = element_blank(),
            legend.title = element_blank(),
            legend.position = "top"
        ) + scale_color_brewer(palette = "Set1")
    ggplotly(p)
}

plot_duplication <- function(d){
    d <- d %>%
        pivot_longer(-`Duplication Level`, names_to = "group", values_to = "percent") ##%>%
        ##mutate(text=paste0("Duplication Level: ", `Duplication Level`, "<br>", "Percent: ", label_percent(0.01)(percent/100)))
    p <- ggplot(d, aes(`Duplication Level`, 
                       percent, 
                       group=group, 
                       color=group))+ 
                       ##text=text))+
        geom_line(alpha=0.8) + ylim(0,100) + theme_bw()+
        theme(
            axis.text.x = element_text(face = "bold", color = "black"),
            panel.grid = element_blank(),
            legend.title = element_blank(),
            legend.position = "top"
        ) + scale_color_brewer(palette = "Set1")
    ggplotly(p) %>% layout(legend = list(x=0.75, y=0.95, title = ""))
}

plot_adapter_content <- function(d){
    d <- d %>% pivot_longer(-Position, names_to = "Adapter", values_to = "percent")
    p <- ggplot(d, aes(Position, percent, color=Adapter))+
        geom_line(alpha=0.8) + ylim(0,100) + 
        theme_bw()+
        theme(
            axis.text.x = element_text(face = "bold", color = "black"),
            panel.grid = element_blank(),
            legend.title = element_blank(),
            legend.position = "top"
        ) + scale_color_brewer(palette = "Set1")
    ggplotly(p) %>% layout(legend = list(x=0.7, y=0.95, title=""))
}
```

## Tools Info

<details>
  <summary>FastQC Version</summary>
  
  ```{bash, echo=FALSE}
  fastqc --version
  ```

</details> 

<details>
  <summary>Cutadapt Version</summary>
  
  ```{bash, echo=FALSE}
  cutadapt --version
  ```
  
</details>

<details>
  <summary>Cutadapt Version</summary>
 
 ```{r comment='', echo=FALSE}
 cat(readLines(params$cutadapt_cmd), sep = '\n')
 ```

</details>

## Statistics

```{r echo=FALSE, message = FALSE, warning = FALSE}
read1_before_stats <- read_tsv(file.path(params$read1_before_dir, "Basic_Statistics"))
read1_after_stats <- read_tsv(file.path(params$read1_after_dir, "Basic_Statistics"))
read2_before_stats <- read_tsv(file.path(params$read2_before_dir, "Basic_Statistics"))
read2_after_stats <- read_tsv(file.path(params$read2_after_dir, "Basic_Statistics"))
read1_stats <- full_join(read1_before_stats, read1_after_stats, by="Measure") %>% dplyr::rename(read1_before=Value.x, read1_after=Value.y)
read2_stats <- full_join(read2_before_stats, read2_after_stats, by="Measure") %>% dplyr::rename(read2_before=Value.x, read2_after=Value.y)
stats <- full_join(read1_stats, read2_stats, by="Measure")
knitr::kable(stats)
```

## Read1 Result

### Before Trimming

#### Quality

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read1_before_quality <- read_tsv(file.path(params$read1_before_dir, "Per_base_sequence_quality"))
plot_quality(read1_before_quality)
```

#### Nucleotides Dirstribution

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read1_before_nt <- read_tsv(file.path(params$read1_before_dir, "Per_base_sequence_content"))
plot_nt_distribution(read1_before_nt)
```

#### Sequence Length Distribution

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read1_before_length <- read_tsv(file.path(params$read1_before_dir, "Sequence_Length_Distribution"))
plot_length(read1_before_length)
```

#### Sequence Duplication Levels

```{r echo=FALSE, message = FALSE, warning = FALSE}
read1_before_duplicationTotal <- read_tsv(file.path(params$read1_before_dir, "Sequence_Duplication_Levels"), 
                                          n_max=1,
                                          col_names = c("term", "value")) %>% pull(value)
```
Percent of seqs remaining if deduplicated: <strong>`r label_percent(0.01)(read1_before_duplicationTotal/100)`</strong>

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read1_before_duplication <- read_tsv(file.path(params$read1_before_dir, "Sequence_Duplication_Levels"), skip=1) %>%
    mutate(`Duplication Level` = factor(`Duplication Level`, levels = `Duplication Level`))
plot_duplication(read1_before_duplication)
```

#### Overrepresented sequences

```{r include=FALSE, message = FALSE, warning = FALSE}
read1_before_overrepresentedTest <- file.exists(file.path(params$read1_before_dir, "Overrepresented_sequences"))
```

```{r echo=FALSE, eval=read1_before_overrepresentedTest, message = FALSE, warning = FALSE}
read1_before_overrepresentedSeq <- read_tsv(file.path(params$read1_before_dir, "Overrepresented_sequences"))
knitr::kable(read1_before_overrepresentedSeq)
```

```{block echo=!read1_before_overrepresentedTest}
No overrepresented sequences
```

#### Adapter Cotent

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read1_before_adapter <- read_tsv(file.path(params$read1_before_dir, "Adapter_Content"))
plot_adapter_content(read1_before_adapter)
```

### After Trimming

#### Quality

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read1_after_quality <- read_tsv(file.path(params$read1_after_dir, "Per_base_sequence_quality"))
plot_quality(read1_after_quality)
```

#### Nucleotides Dirstribution

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read1_after_nt <- read_tsv(file.path(params$read1_after_dir, "Per_base_sequence_content"))
plot_nt_distribution(read1_after_nt)
```

#### Sequence Length Distribution

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read1_after_length <- read_tsv(file.path(params$read1_after_dir, "Sequence_Length_Distribution"))
plot_length(read1_after_length)
```

#### Sequence Duplication Levels

```{r echo=FALSE, message = FALSE, warning = FALSE}
read1_after_duplicationTotal <- read_tsv(file.path(params$read1_after_dir, "Sequence_Duplication_Levels"), 
                                          n_max=1,
                                          col_names = c("term", "value")) %>% pull(value)
```
Percent of seqs remaining if deduplicated: <strong>`r label_percent(0.01)(read1_after_duplicationTotal/100)`</strong>

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read1_after_duplication <- read_tsv(file.path(params$read1_after_dir, "Sequence_Duplication_Levels"), skip=1) %>%
    mutate(`Duplication Level` = factor(`Duplication Level`, levels = `Duplication Level`))
plot_duplication(read1_after_duplication)
```

#### Overrepresented sequences

```{r include=FALSE, message = FALSE, warning = FALSE}
read1_after_overrepresentedTest <- file.exists(file.path(params$read1_after_dir, "Overrepresented_sequences"))
```

```{r echo=FALSE, eval=read1_after_overrepresentedTest, message = FALSE, warning = FALSE}
read1_after_overrepresentedSeq <- read_tsv(file.path(params$read1_after_dir, "Overrepresented_sequences"))
knitr::kable(read1_after_overrepresentedSeq)
```

```{block echo=!read1_after_overrepresentedTest}
No overrepresented sequences
```

#### Adapter Cotent

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read1_after_adapter <- read_tsv(file.path(params$read1_after_dir, "Adapter_Content"))
plot_adapter_content(read1_after_adapter)
```

## Read2 Result

### Before Trimming

#### Quality

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read2_before_quality <- read_tsv(file.path(params$read2_before_dir, "Per_base_sequence_quality"))
plot_quality(read2_before_quality)
```

#### Nucleotides Dirstribution

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read2_before_nt <- read_tsv(file.path(params$read2_before_dir, "Per_base_sequence_content"))
plot_nt_distribution(read2_before_nt)
```

#### Sequence Length Distribution

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read2_before_length <- read_tsv(file.path(params$read2_before_dir, "Sequence_Length_Distribution"))
plot_length(read2_before_length)
```

#### Sequence Duplication Levels

```{r echo=FALSE, message = FALSE, warning = FALSE}
read2_before_duplicationTotal <- read_tsv(file.path(params$read2_before_dir, "Sequence_Duplication_Levels"), 
                                          n_max=1,
                                          col_names = c("term", "value")) %>% pull(value)
```
Percent of seqs remaining if deduplicated: <strong>`r label_percent(0.01)(read2_before_duplicationTotal/100)`</strong>

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read2_before_duplication <- read_tsv(file.path(params$read2_before_dir, "Sequence_Duplication_Levels"), skip=1) %>%
    mutate(`Duplication Level` = factor(`Duplication Level`, levels = `Duplication Level`))
plot_duplication(read2_before_duplication)
```

#### Overrepresented sequences

```{r include=FALSE, message = FALSE, warning = FALSE}
read2_before_overrepresentedTest <- file.exists(file.path(params$read2_before_dir, "Overrepresented_sequences"))
```

```{r echo=FALSE, eval=read2_before_overrepresentedTest, message = FALSE, warning = FALSE}
read2_before_overrepresentedSeq <- read_tsv(file.path(params$read2_before_dir, "Overrepresented_sequences"))
knitr::kable(read2_before_overrepresentedSeq)
```

```{block echo=!read2_before_overrepresentedTest}
No overrepresented sequences
```

#### Adapter Cotent

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read2_before_adapter <- read_tsv(file.path(params$read2_before_dir, "Adapter_Content"))
plot_adapter_content(read2_before_adapter)
```

### After Trimming

#### Quality

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read2_after_quality <- read_tsv(file.path(params$read2_after_dir, "Per_base_sequence_quality"))
plot_quality(read2_after_quality)
```

#### Nucleotides Dirstribution

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read2_after_nt <- read_tsv(file.path(params$read2_after_dir, "Per_base_sequence_content"))
plot_nt_distribution(read2_after_nt)
```

#### Sequence Length Distribution

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read2_after_length <- read_tsv(file.path(params$read2_after_dir, "Sequence_Length_Distribution"))
plot_length(read2_after_length)
```

#### Sequence Duplication Levels

```{r echo=FALSE, message = FALSE, warning = FALSE}
read2_after_duplicationTotal <- read_tsv(file.path(params$read2_after_dir, "Sequence_Duplication_Levels"), 
                                          n_max=1,
                                          col_names = c("term", "value")) %>% pull(value)
```
Percent of seqs remaining if deduplicated: <strong>`r label_percent(0.01)(read2_after_duplicationTotal/100)`</strong>

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read2_after_duplication <- read_tsv(file.path(params$read2_after_dir, "Sequence_Duplication_Levels"), skip=1) %>%
    mutate(`Duplication Level` = factor(`Duplication Level`, levels = `Duplication Level`))
plot_duplication(read2_after_duplication)
```

#### Overrepresented sequences

```{r include=FALSE, message = FALSE, warning = FALSE}
read2_after_overrepresentedTest <- file.exists(file.path(params$read2_after_dir, "Overrepresented_sequences"))
```

```{r echo=FALSE, eval=read2_after_overrepresentedTest, message = FALSE, warning = FALSE}
read2_after_overrepresentedSeq <- read_tsv(file.path(params$read2_after_dir, "Overrepresented_sequences"))
knitr::kable(read2_after_overrepresentedSeq)
```

```{block echo=!read2_after_overrepresentedTest}
No overrepresented sequences
```

#### Adapter Cotent

```{r echo=FALSE, out.width="100%", message = FALSE, warning = FALSE}
read2_after_adapter <- read_tsv(file.path(params$read2_after_dir, "Adapter_Content"))
plot_adapter_content(read2_after_adapter)
```
